\textbf{Using the MSU Thesis Class}

### 2021-06-08 msu-thesis.tex

The latest copy of \pkg{msu-thesis} will always be available on  \href{https://ctan.org/pkg/msu-thesis?lang=en}{CTAN}. If you use MiKTeX, or a current year TeX Live then their respective package managers will update or install the latest version. If you are using Overleaf, you may or may not have the most recent version, since Overleaf is usually about one year behind in it’s TeX distribution.  If you are using a Linux-based distribution, or your TeXLive distribution is not the most recent year, you may need to install the latest copy in your local |texmf| directory. If you want others to use the class, \textsc{please} point them to CTAN, or tell them to use an up-to-date TeX distribution so that they can use an up-to-date version with all accompanying documentation and examples rather than passing along your copy. Please report \textsc{any} problems you have with the class to me \href{mailto:amunn@msu.edu}{amunn@msu.edu}, as this will aid in making things easier for those who follow you. If you prefer, you may also report issues using GitHub: \href{https://github.com/amunn/msu-thesis}{github.com/amunn/msu-thesis}.  The Graduate School rarely announces changes it makes to the formatting requirements, so your problem reports are extremely helpful for keeping the class in compliance with the latest standards.

@@

Previous versions of \pkg{msu-thesis} (versions 1.0--1.4b) were created for non-electronic submission and should not be used. Versions 1.5--1.6 (the first electronic submission versions) contained a |\makeabstract| command and a separate |msuabstract| environment. These have been removed as of version 1.7.  Users who are upgrading from earlier versions to version 1.7 do not need to change these commands however but their use will trigger a warning.) Version 2.0 implemented landscape pages; version 2.1 added support for \pkg{hyperref}. Versions 2.2--2.5 mainly accommodated to the ever changing whims of the MSU Graduate School. Version 2.6 fixed some appendix bugs introduced by the previous whim accommodation. Version 2.7 fixed various small spacing issues, fixed a bug which prevented a new chapter page to be a landscape page, added support for the \pkg{apacite} package, and updated degree options. Version 2.8 fixed some spacing and capitalization issues and added support for the the public abstract. Version 2.9 removed subscript/superscript size restrictions, added font size options and made small spacing changes to appease the thesis office.

@@

Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex} spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version, and Florent Chervet for the hyperref code. Thanks also to the following students who have reported problems over the years: Irina Agafonova, Ali Al-jiboory, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Matt Husband, Changkuk Jung, Adam Liter, William Muir, Adam Soliman, Alicia Parrish, Neil ver Planck, Michael Wojcik, Eremey Valetov, Matthew Vincent and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy of his entire thesis which allowed me to debug some especially subtle spacing inconsistencies.

>>>>

The latest copy of \pkg{msu-thesis} will always be available on  \href{https://ctan.org/pkg/msu-thesis?lang=en}{CTAN}. If you use MiKTeX, or a current year TeX Live then their respective package managers will update or install the latest version. If you are using Overleaf, you may or may not have the most recent version, since Overleaf is usually about one year behind in its TeX distribution.  If you are using a Linux-based distribution, or your TeXLive distribution is not the most recent year, you may need to install the latest copy in your local |texmf| directory. If you want others to use the class, \textsc{please} point them to CTAN, or tell them to use an up-to-date TeX distribution so that they can use an up-to-date version with all accompanying documentation and examples rather than passing along your copy. Please report \textsc{any} problems you have with the class to me \href{mailto:amunn@msu.edu}{amunn@msu.edu}, as this will aid in making things easier for those who follow you. If you prefer, you may also report issues using GitHub: \href{https://github.com/amunn/msu-thesis}{github.com/amunn/msu-thesis}.  The Graduate School rarely announces changes it makes to the formatting requirements, so your problem reports are extremely helpful for keeping the class in compliance with the latest standards.

@@

Previous versions of \pkg{msu-thesis} (versions 1.0--1.4b) were created for non-electronic submission and should not be used. Versions 1.5--1.6 (the first electronic submission versions) contained a |\makeabstract| command and a separate |msuabstract| environment. These have been removed as of version 1.7.  Users who are upgrading from earlier versions to version 1.7 do not need to change these commands however but their use will trigger a warning.) Version 2.0 implemented landscape pages; version 2.1 added support for \pkg{hyperref}. Versions 2.2--2.5 mainly accommodated to the ever changing whims of the MSU Graduate School. Version 2.6 fixed some appendix bugs introduced by the previous whim accommodation. Version 2.7 fixed various small spacing issues, fixed a bug which prevented a new chapter page to be a landscape page, added support for the \pkg{apacite} package, and updated degree options. Version 2.8 fixed some spacing and capitalization issues and added support for the public abstract. Version 2.9 removed subscript/superscript size restrictions, added font size options and made small spacing changes to appease the thesis office.

@@

Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex} spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version, and Florent Chervet for the \pkg{hyperref} code. Thanks also to the following students who have reported problems over the years: Irina Agafonova, Ali Al-jiboory, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Matt Husband, Changkuk Jung, Adam Liter, William Muir, Adam Soliman, Alicia Parrish, Neil ver Planck, Michael Wojcik, Eremey Valetov, Matthew Vincent and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy of his entire thesis which allowed me to debug some especially subtle spacing inconsistencies.
